---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cellphaseR

<!-- badges: start -->
<!-- badges: end -->

cellphaseR is an R package for the analysis of cell cycle experiments generated on the BioTek Cytation platform. It is primarily an implementation of [ggplot2](https://cran.r-project.org/web/packages/ggplot2/index.html) and [ggridges](https://cran.r-project.org/web/packages/ggridges/index.html) packages for visualization and analysis of object level DNA content measurements by propidium iodide (PI) staining. Although not tested here, this package should be applicable to any other staining methods that are indicative of relative DNA content.

## Installation

You can install the development version of cellphaseR as follows:

``` r
# install.packages("devtools")
devtools::install_github("HGWithers/cellphaseR")
```

## Example Dataset

An example dataset `PIdata` is provided with the package and contains imaging data for PI stained cells from two different cell types: wildtype (WT) mouse embryonic fibroblasts (wtMEF) or p53 knockout MEFs transduced with HRas-V12-GFP oncogene.

```{r example}
## Load the library
library(cellphaseR)

## View the example dataset
PIdata
```

## Visualizing Cell Cycle Data
The `cpridges` function generates a histogram with kernel density estimate overlay for your DNA content data. Here we use the `PI Obj Integral` output value from the example `PIdata` to plot cell cycle data by each cell type (`group = Cells`) 

```{r cpridges_base_example, dpi = 300, out.width = "80%"}
cpridges(data = PIdata, signal = `PI Obj Integral`, group = Cells)
```

### Customizing `cpridges`
The position of peaks can be labeled using the `label.peaks` argument of `cpridges` and refined using the `peak.threshold` argument. Arguments are also available to adjust histogram bins or log~10~ transform the x-axis. Additional ggplot2 functions can be appended to `cpridges` for customization of plots.

```{r cpridges_options_example, dpi = 300, out.width = "50%", fig.show = "hold"}
cpridges(data = PIdata, signal = `PI Obj Integral`, group = Cells,
         label.peaks = TRUE, peak.threshold = 0) + ggplot2::labs(title = "Peak threshold = 0.0")
cpridges(data = PIdata, signal = `PI Obj Integral`, group = Cells,
         label.peaks = TRUE, peak.threshold = 0.1) + ggplot2::labs(title = "Peak threshold = 0.1")
```
